{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-10-12 sftrends_manu.tex
fixed label error in trnd_map function
updating data from new wrtds preds

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Tue Jul 19 17:50:17 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption[Nitrogen load measurements (kg d]{Nitrogen load measurements (kg d$^{-1}$) at the City of Tracy Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in May, 2007 to include nitrification/denitrification and tertiary filtration causing a reduction in total nitrogen effluent discharged to the Delta. Reductions were primarily observed for ammonium.}\label{fig:tracy}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figs/p8trnds-1}

\caption{Nitrogen trends at P8 as observed (a, top), predicted and flow-normalized estimates from \ac{wrtds} (a, bottom), and relationships with flow over time (b).  Nitrite/nitrate trends are on the left and ammonium trends are on the right.  Wastewater treatment plant upgrades at the City of Tracy (San Joaquin County), were completed in May 2007 (\cref{fig:tracy}), coincident with a dramatic decrease in ammonium at P8.}\label{fig:p8trnds}
\end{figure}

@@

{\centering \includegraphics[width=\maxwidth]{figs/d7c10trnds-1}

\caption{Flow-normalized trends of annual (left) and seasonal (right) variation in DIN, chl-{\it\footnotesize a}, and SiO$_2$ at station D7 (top) and C10 (bottom).  Covariation between nutrients, chl-{\it\footnotesize a}, and SiO$_2$ is observed at D7 but not C10, although an overall decrease in SiO$_2$ at C10 is shown.  Seasonal changes at D7 are most pronounced during the summer.}\label{fig:d7c10trnds}
\end{figure}

@@

% trends in no23, nh at p8
%latex.default(totab, file = "", rowlabel = "Period", caption = cap.val,     caption.loc = "top", rgroup = segs, n.rgroup = c(2, rep(4,         2)), cgroup = vars, n.cgroup = c(2, 2), rowname = cats,     label = "tab:p8chg")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrite/nitrate and ammonium (mg L$^{-1}$) concentrations before and after \ac{wwtp} upgrades upstream of station P8. Upgrades were completed in May 2007 at the City of Tracy \ac{wwtp} (San Joaquin County, \cref{fig:tracy}).  Summaries are means and percent changes based on annual means within the pre- and post-upgrade time periods (1976-2007, 2008-2013).  Increasing values are in bold-italics.\label{tab:p8chg}} 
\begin{center}
\begin{tabular}{lllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Period}&\multicolumn{2}{c}{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NH$_{4}^{+}$}\tabularnewline
\cline{2-3} \cline{5-6}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{\% change}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{\% change}\tabularnewline
\hline
{\bfseries Annual}&&&&&\tabularnewline
~~1976-2007&1.27&\textit{\textbf{75.7}}&&0.33&\textit{\textbf{71.3}}\tabularnewline
~~2008-2013&1.47&-6&&0.11&-62.6\tabularnewline
\hline
{\bfseries Seasonal, pre}&&&&&\tabularnewline
~~JFM&1.46&\textit{\textbf{77.7}}&&0.49&\textit{\textbf{57.1}}\tabularnewline
~~AMJ&1&\textit{\textbf{75.3}}&&0.13&\textit{\textbf{63.4}}\tabularnewline
~~JAS&1.08&\textit{\textbf{97.9}}&&0.13&\textit{\textbf{151.9}}\tabularnewline
~~OND&1.53&\textit{\textbf{81.9}}&&0.54&\textit{\textbf{102.4}}\tabularnewline
\hline
{\bfseries Seasonal, post}&&&&&\tabularnewline
~~JFM&1.76&-3.4&&0.14&-47\tabularnewline
~~AMJ&0.94&-5.5&&0.07&-45.3\tabularnewline
~~JAS&1.17&-10&&0.07&-50.3\tabularnewline
~~OND&1.99&-4.6&&0.15&-58.5\tabularnewline
\hline
\end{tabular}\end{center}

>>>>

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

@@

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Fri Sep 30 17:57:52 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption[Nitrogen load measurements (kg d$^{-1}$) at the City of Tracy Wastewater Treatment Plant, San Joaquin County]{Nitrogen load measurements (kg d$^{-1}$) at the City of Tracy Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in May, 2007 to include nitrification/denitrification and tertiary filtration causing a reduction in total nitrogen effluent discharged to the Delta. Reductions were primarily observed for ammonium.}\label{fig:tracy}
\end{figure}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}select\_"{}): no applicable method for 'select\_' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}select\_"{}): no applicable method for 'select\_' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Invalid input: date\_trans works with objects of class Date only}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Invalid input: date\_trans works with objects of class Date only}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in tmp\$grobs[[leg]]: attempt to select less than one element in get1index}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}dynaplot"{}): no applicable method for 'dynaplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'p5' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'p5' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}dynaplot"{}): no applicable method for 'dynaplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'p5' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'p6' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unit.pmax(pA\$widths[2:3], pB\$widths[2:3], pC\$widths[2:3], pD\$widths[2:3], : object 'pE' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pE\$widths[2:3] <- maxWidth: object 'pE' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pF\$widths[2:3] <- maxWidth: object 'pF' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrangeGrob(...): object 'pleg1' not found}}\end{kframe}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}select\_"{}): no applicable method for 'select\_' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): 'yr' column not found in lhs, cannot join}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'bt\_norm' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in seq.default(xvals[1], xvals[2], length = 100): 'from' cannot be NA, NaN or infinite}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}dynaplot"{}): no applicable method for 'dynaplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'biomass' not found}}\end{kframe}\begin{figure}[!ht]

@@

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdin1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'pdin1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdinsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'pdinsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdin1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pchl1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'psio1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unit.pmax(pA1\$widths[2:3], pB1\$widths[2:3], pC1\$widths[2:3]): object 'pA1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pA1\$widths[2:3] <- maxWidth: object 'pA1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pB1\$widths[2:3] <- maxWidth: object 'pB1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pC1\$widths[2:3] <- maxWidth: object 'pC1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdinsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pchlsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'psiosy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unit.pmax(pAsy1\$widths[2:3], pBsy1\$widths[2:3], pCsy1\$widths[2:3]): object 'pAsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pAsy1\$widths[2:3] <- maxWidth: object 'pAsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pBsy1\$widths[2:3] <- maxWidth: object 'pBsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pCsy1\$widths[2:3] <- maxWidth: object 'pCsy1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}prdnrmplot"{}): no applicable method for 'prdnrmplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}seasyrplot"{}): no applicable method for 'seasyrplot' applied to an object of class "{}NULL"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdin2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pchl2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'psio2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unit.pmax(pA2\$widths[2:3], pB2\$widths[2:3], pC2\$widths[2:3]): object 'pA2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pA2\$widths[2:3] <- maxWidth: object 'pA2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pB2\$widths[2:3] <- maxWidth: object 'pB2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pC2\$widths[2:3] <- maxWidth: object 'pC2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pdinsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'pchlsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_clone(plot): object 'psiosy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unit.pmax(pAsy2\$widths[2:3], pBsy2\$widths[2:3], pCsy2\$widths[2:3]): object 'pAsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pAsy2\$widths[2:3] <- maxWidth: object 'pAsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pBsy2\$widths[2:3] <- maxWidth: object 'pBsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pCsy2\$widths[2:3] <- maxWidth: object 'pCsy2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrangeGrob(pleg1, pleg2, ncol = 2): object 'pleg1' not found}}\end{kframe}

@@

% overall trends
%latex.default(tab[, -c(1, 2)], file = "", rowlabel = "Analyte/Station",     caption = cap.val, caption.loc = "top", rgroup = vars, n.rgroup = c(9,         9, 9), cgroup = c("Annual", "Seasonal"), n.cgroup = c(3,         3), rowname = stats, label = "tab:trnds")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrogen analytes for all stations and different time periods.  Summaries are averages (mg L$^{-1}$) and percent changes in parentheses (increasing in bold-italic).  Changes are based on the difference between the ending and starting estimates for the estimates within each period.  See \cref{fig:trndmap} for a summary of spatial trends.\label{tab:trnds}} 
\begin{center}
\begin{tabular}{llllclll}
\hline\hline
\multicolumn{1}{l}{\bfseries Analyte/Station}&\multicolumn{3}{c}{\bfseries Annual}&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Seasonal}\tabularnewline
\cline{2-4} \cline{6-8}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{1976-1988}&\multicolumn{1}{c}{1989-2000}&\multicolumn{1}{c}{2001-2012}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{JFMA}&\multicolumn{1}{c}{MJJA}&\multicolumn{1}{c}{SOND}\tabularnewline
\hline
{\bfseries DIN}&&&&&&&\tabularnewline
~~C10&1.3 \footnotesize{(\textit{\textbf{29.9}})}&1.4 \footnotesize{(\textit{\textbf{17.6}})}&1.3 \footnotesize{(-39)}&&1.4 \footnotesize{(-25.6)}&1.1 \footnotesize{(-10)}&1.5 \footnotesize{(-0.2)}\tabularnewline
~~C3&0.3 \footnotesize{(\textit{\textbf{31}})}&0.4 \footnotesize{(\textit{\textbf{23.5}})}&0.5 \footnotesize{(-7.9)}&&0.4 \footnotesize{(\textit{\textbf{29.5}})}&0.4 \footnotesize{(\textit{\textbf{78.8}})}&0.5 \footnotesize{(\textit{\textbf{45.1}})}\tabularnewline
~~D19&0.5 \footnotesize{(-16.5)}&0.5 \footnotesize{(\textit{\textbf{7}})}&0.4 \footnotesize{(-27.5)}&&0.7 \footnotesize{(-35.9)}&0.3 \footnotesize{(-25.5)}&0.4 \footnotesize{(-24.6)}\tabularnewline
~~D26&0.4 \footnotesize{(-12)}&0.5 \footnotesize{(\textit{\textbf{11.5}})}&0.4 \footnotesize{(-19.8)}&&0.6 \footnotesize{(-24.6)}&0.3 \footnotesize{(-9.7)}&0.4 \footnotesize{(-6.7)}\tabularnewline
~~D28&0.5 \footnotesize{(-16.7)}&0.5 \footnotesize{(\textit{\textbf{5.9}})}&0.4 \footnotesize{(-41.1)}&&0.7 \footnotesize{(-35.8)}&0.3 \footnotesize{(-49)}&0.4 \footnotesize{(-52.3)}\tabularnewline
~~D4&0.4 \footnotesize{(-23.7)}&0.4 \footnotesize{(\textit{\textbf{23.7}})}&0.4 \footnotesize{(-8.4)}&&0.5 \footnotesize{(-14.3)}&0.3 \footnotesize{(\textit{\textbf{1.7}})}&0.4 \footnotesize{(\textit{\textbf{1.6}})}\tabularnewline
~~D6&0.4 \footnotesize{(-9)}&0.5 \footnotesize{(\textit{\textbf{22.6}})}&0.5 \footnotesize{(-7.8)}&&0.5 \footnotesize{(-15.8)}&0.4 \footnotesize{(\textit{\textbf{51}})}&0.4 \footnotesize{(\textit{\textbf{18.9}})}\tabularnewline
~~D7&0.4 \footnotesize{(-21.5)}&0.5 \footnotesize{(\textit{\textbf{22.9}})}&0.5 \footnotesize{(-10.1)}&&0.5 \footnotesize{(-29.9)}&0.4 \footnotesize{(\textit{\textbf{28.5}})}&0.4 \footnotesize{(-0.2)}\tabularnewline
~~P8&1.2 \footnotesize{(\textit{\textbf{60.1}})}&1.7 \footnotesize{(\textit{\textbf{36.7}})}&1.8 \footnotesize{(-32.7)}&&1.9 \footnotesize{(\textit{\textbf{37}})}&1.1 \footnotesize{(\textit{\textbf{39.1}})}&1.8 \footnotesize{(\textit{\textbf{50.1}})}\tabularnewline
\hline
{\bfseries NH$_{4}^{+}$}&&&&&&&\tabularnewline
~~C10&0.2 \footnotesize{(-20.2)}&0.1 \footnotesize{(-54.7)}&0 \footnotesize{(-23.2)}&&0.1 \footnotesize{(-73.6)}&0 \footnotesize{(-81.8)}&0.1 \footnotesize{(-87.9)}\tabularnewline
~~C3&0.2 \footnotesize{(\textit{\textbf{88.5}})}&0.3 \footnotesize{(\textit{\textbf{35.9}})}&0.3 \footnotesize{(-3.3)}&&0.2 \footnotesize{(\textit{\textbf{113}})}&0.3 \footnotesize{(\textit{\textbf{150.4}})}&0.3 \footnotesize{(\textit{\textbf{101.1}})}\tabularnewline
~~D19&0.1 \footnotesize{(\textit{\textbf{29.6}})}&0.1 \footnotesize{(-10.7)}&0.1 \footnotesize{(-19.8)}&&0.1 \footnotesize{(-24.4)}&0 \footnotesize{(-22.4)}&0.1 \footnotesize{(-2.8)}\tabularnewline
~~D26&0.1 \footnotesize{(\textit{\textbf{43.6}})}&0.1 \footnotesize{(-0.1)}&0.1 \footnotesize{(-12.7)}&&0.1 \footnotesize{(-3.8)}&0.1 \footnotesize{(\textit{\textbf{34.6}})}&0.1 \footnotesize{(\textit{\textbf{17.1}})}\tabularnewline
~~D28&0.1 \footnotesize{(-15.5)}&0.1 \footnotesize{(-14.9)}&0 \footnotesize{(-16.2)}&&0.1 \footnotesize{(-42.3)}&0 \footnotesize{(-34.8)}&0.1 \footnotesize{(-35.2)}\tabularnewline
~~D4&0.1 \footnotesize{(\textit{\textbf{17.3}})}&0.1 \footnotesize{(\textit{\textbf{64}})}&0.1 \footnotesize{(-2.9)}&&0.1 \footnotesize{(\textit{\textbf{71.7}})}&0 \footnotesize{(\textit{\textbf{36.8}})}&0.1 \footnotesize{(\textit{\textbf{39}})}\tabularnewline
~~D6&0.1 \footnotesize{(\textit{\textbf{55.4}})}&0.1 \footnotesize{(\textit{\textbf{31.1}})}&0.1 \footnotesize{(-5.7)}&&0.1 \footnotesize{(\textit{\textbf{44.1}})}&0.1 \footnotesize{(\textit{\textbf{69.8}})}&0.1 \footnotesize{(\textit{\textbf{56}})}\tabularnewline
~~D7&0.1 \footnotesize{(\textit{\textbf{36}})}&0.1 \footnotesize{(\textit{\textbf{35.6}})}&0.1 \footnotesize{(-6.1)}&&0.1 \footnotesize{(\textit{\textbf{36.5}})}&0 \footnotesize{(\textit{\textbf{27.2}})}&0.1 \footnotesize{(\textit{\textbf{11.5}})}\tabularnewline
~~P8&0.2 \footnotesize{(\textit{\textbf{186.1}})}&0.4 \footnotesize{(\textit{\textbf{47.1}})}&0.2 \footnotesize{(-86.8)}&&0.4 \footnotesize{(-58.9)}&0.1 \footnotesize{(-21.8)}&0.3 \footnotesize{(-51.9)}\tabularnewline
\hline
{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&&&&&&&\tabularnewline
~~C10&1.2 \footnotesize{(\textit{\textbf{34.1}})}&1.4 \footnotesize{(\textit{\textbf{23.3}})}&1.3 \footnotesize{(-39.1)}&&1.3 \footnotesize{(-16.4)}&1.1 \footnotesize{(-6)}&1.4 \footnotesize{(\textit{\textbf{18.7}})}\tabularnewline
~~C3&0.1 \footnotesize{(-7.3)}&0.2 \footnotesize{(\textit{\textbf{6.5}})}&0.2 \footnotesize{(-9.6)}&&0.2 \footnotesize{(-14)}&0.1 \footnotesize{(\textit{\textbf{20.7}})}&0.2 \footnotesize{(-2.9)}\tabularnewline
~~D19&0.4 \footnotesize{(-23.7)}&0.4 \footnotesize{(\textit{\textbf{9}})}&0.4 \footnotesize{(-28.1)}&&0.6 \footnotesize{(-37.3)}&0.3 \footnotesize{(-33.4)}&0.4 \footnotesize{(-33.7)}\tabularnewline
~~D26&0.3 \footnotesize{(-21.4)}&0.4 \footnotesize{(\textit{\textbf{14.2}})}&0.3 \footnotesize{(-21.6)}&&0.5 \footnotesize{(-28.6)}&0.3 \footnotesize{(-17.4)}&0.3 \footnotesize{(-13.2)}\tabularnewline
~~D28&0.4 \footnotesize{(-22)}&0.5 \footnotesize{(\textit{\textbf{5.6}})}&0.4 \footnotesize{(-43.7)}&&0.6 \footnotesize{(-38.5)}&0.3 \footnotesize{(-57.9)}&0.4 \footnotesize{(-59.7)}\tabularnewline
~~D4&0.3 \footnotesize{(-26.5)}&0.3 \footnotesize{(\textit{\textbf{15.8}})}&0.3 \footnotesize{(-9.3)}&&0.4 \footnotesize{(-23.4)}&0.3 \footnotesize{(-1.7)}&0.3 \footnotesize{(-7.3)}\tabularnewline
~~D6&0.3 \footnotesize{(-22.6)}&0.4 \footnotesize{(\textit{\textbf{19.6}})}&0.4 \footnotesize{(-8.5)}&&0.4 \footnotesize{(-25.1)}&0.3 \footnotesize{(\textit{\textbf{30.3}})}&0.3 \footnotesize{(\textit{\textbf{2.8}})}\tabularnewline
~~D7&0.4 \footnotesize{(-30.1)}&0.4 \footnotesize{(\textit{\textbf{19.3}})}&0.4 \footnotesize{(-11.3)}&&0.4 \footnotesize{(-35.6)}&0.3 \footnotesize{(\textit{\textbf{12.7}})}&0.4 \footnotesize{(-30.6)}\tabularnewline
~~P8&1.1 \footnotesize{(\textit{\textbf{46}})}&1.3 \footnotesize{(\textit{\textbf{30.4}})}&1.6 \footnotesize{(-16.3)}&&1.5 \footnotesize{(\textit{\textbf{60}})}&1 \footnotesize{(\textit{\textbf{40}})}&1.5 \footnotesize{(\textit{\textbf{60}})}\tabularnewline
\hline
\end{tabular}\end{center}
